%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Zainalabdeen Al-Saffi} \\ \vspace{1pt}
    \small 0401-107-566 $|$ \href{zainalsaffi@gmail.com}{\underline{zainalsaffi@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/zain-al-saffi-881492250/}{\underline{linkedin.com/zain-al-saffi}} $|$
    \href{https://github.com/TheNoZer0}{\underline{github.com/TheNoZER0}}
\end{center}

\vspace{-20pt}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Queensland}{St Lucia QLD}
      {Bachelor of Economics / Computer Science (Quant and Machine Learning Major)}{Feb. 2024 -- October 2027}
    \resumeItemListStart
      
        \resumeItem{\textbf{GPA:} 6.75/7.00 (Deans Academic Excellence Award 2025)}
      
       \resumeItem{Treasurer -  UQ Computing Society}
       \resumeItem{General Executive - UQ Fintech}
      
      \resumeItemListEnd
    
      
  \resumeSubHeadingListEnd
   
 
%-----------EXPERIENCE-----------
\section{Experience}
 \resumeSubHeadingListStart

    \resumeSubheading
      {Thiess}{South Bank QLD}
      {\textbf{Data Science Intern}}{Dec. 2024 -- Feb.2025}
      \resumeItemListStart
        \resumeItem{Developed a statistical learning state machine using Gaussian Mixture Models and IMM-EKF for real-time truck operation classification and sensor fusion, enhancing reliability and reducing costs by 20\% .}
        \resumeItem{Conducted extensive data cleaning and feature engineering using PySpark, SQL, and Jupyter Notebooks, including joining disparate telemetry datasets and modelling sensor noise. . }
        \resumeItem{Developed a linear model to correct timestamp misalignment, ensuring synchronisation across data sources. Optimised GMM performance via BIC, AIC, Elbow Method, Calinski-Harabasz Index, and the EM algorithm}
        
        \resumeItem{Integrated a domain-specific penalty matrix with the Viterbi algorithm to constrain improbable state transitions, improving classification accuracy and operational efficiency. }
      \resumeItemListEnd
      
  

    \resumeSubheading
      {UQ Racing}{St Lucia QLD}
      {\textbf{Lead Software Engineer}} {Nov. 2024 -- June 2025}
      \resumeItemListStart
        \resumeItem{Led ROS-to-ROS2 migration in Python and C++, integrating TensorRT-quantised YOLOv11 for faster, more accurate cone detection in real-time autonomous navigation. }
        \resumeItem{Built a Dockerised ROS2-Gazebo simulation environment enabling remote development and virtual testing, boosting testing availability by 80\% and accelerating R\&D deployment. }
        \resumeItem{Researched and experimented with advanced sensor fusion techniques (EKF, UKF) and FAST-LIO SLAM to produce high-fidelity simulation maps of test tracks. }
        \resumeItem{Introduced a task-ranked project management system with strategic resource planning and regular stand-ups, eliminating missed deadlines and making the software team the project’s top performer. }

      \resumeItemListEnd

     \vspace{-15pt}
    \resumeSubheading
        {} {}{\textbf{Software Engineer}}{Feb. 2024 -- Nov. 2024}
      \resumeItemListStart
        \resumeItem{Developed path planning algorithms using a perception stack integrating YOLOv8, Lidar, and INS data with Delaunay Triangulation for track driving.}
        
    \resumeItemListEnd


    
\resumeSubheading
      {University of Queensland}{St Lucia QLD}
      {\textbf{Casual Academic Tutor}}{June. 2025 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{COMP3710 (Pattern Recognition and Analysis): }Instructed 20+ students weekly on machine and deep learning models and techniques }
      \resumeItemListEnd
      \vspace{-10pt}
        
      \resumeSubheading
      {}{St Lucia QLD}
      {\textbf{Student Services Ambassador}}{Jan. 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Assisted students with selection of courses and navigating UQ's proprietary software for enrollments, while representing the university as one of 30 ambassadors }
        \resumeItemListEnd
      \vspace{-10pt}
       \resumeSubheading
      {}{St Lucia QLD}
      {\textbf{Future Students Ambassador}}{Mar. 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Represented the university and EAIT faculty in school expos, talks and careers fairs to guide prospective students in degree selection}
\resumeItemListEnd
   

    
    

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects And Competition Awards}
    \resumeSubHeadingListStart
\resumeProjectHeading
          {\textbf{IMC Prosperity 3} $|$ \emph{Python, Git, Jupyter, Sk-Learn}}{April 2025}
          \resumeItemListStart
            \resumeItem{Applied advanced statistical techniques in a 5-person team during IMC Trading’s global competition, including cointegration and Ornstein-Uhlenbeck modeling for mean-reversion, Black-Scholes-based option pricing, IV curve fitting, and delta-hedging to build robust pairs, basket, and options arbitrage strategies. Developed a custom Python visualiser to automate stationarity checks and monitor real-time PnL, contributing to a \textbf{1st place QLD finish, 9th AU, 60th algorithmic globally out of 15,000 teams)}.  }
            
           
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{ValoStats} $|$ \emph{Python, Streamlit, Jupyter}}{August 2024}
          \resumeItemListStart
            \resumeItem{\textbf{Led a team of 6 engineers to develop ValoStats}, a full-stack web application using Python and Streamlit that integrates RIOT’s API for real-time match data; Kaggle dataset was pulled and featured engineered while implemented Gradient Boosting and Logistic Regression ensemble methods to accurately predict match outcomes with 90\% accuracy, earning the \textbf{People’s Choice Award at the UQ Computing Society Hackathon.} }
           
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AlgoJam} $|$ \emph{Python, Git}}{September 2024}
          \resumeItemListStart
            \resumeItem{\textbf{Coordinated a team of 3 to analyze and strategize financial instruments} for the UQ Fintech Algothon by developing ARIMA time-series models and pair trading strategies, applying exponential moving averages to optimize asset performance, and securing \textbf{third place} in the competition sponsored by IMC Trading }
          
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{SkinDetect} $|$ \emph{Python, Git, Pytorch}}{September 2024}
          \resumeItemListStart
            \resumeItem{\textbf{Designed and implemented a Siamese network with ResNet50 and triplet loss in PyTorch} to classify benign and malignant skin lesions for the ISIC 2020 Challenge, achieving 95\% accuracy; addressed class imbalance through oversampling and balanced batch sampling, utilized CUDA 11.8 for optimized training, and conducted comprehensive evaluations using AUC-ROC and t-SNE visualizations to ensure reliable performance }
           
          \resumeItemListEnd

    
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, JavaScript, TypeScript} \\
     \textbf{Frameworks / SDKs}{: Streamlit, Node.js, JUnit, ROS, gtest, CUDA, TensorRT} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, Visual Studio, PyCharm, IntelliJ, Azure databricks, Jupyter Notebooks} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, pytorch, scitkit-learn, eigen, seaborn, streamlit, pyMLE, statistics}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
